simplex: An individual-based modeling platform

### 2015-10-19 paper/PrePrint.Rmd

---
title: "simplex: An individual-based modeling platform"
author: "Kenneth J Locey,
Dept. of Biology, University of Indiana, Bloomington"
geometry: margin=2.54cm
output: pdf_document
header-includes:
    - \usepackage{setspace}
    - \doublespacing
---

@@

Here, I present source code and a detailed description for an ecological IBM platform (called simplex) that simulates a broad range of ecological conditions, records information from individuals to the ecosystem, and provides computing code for analyzing output. This platform incorporates computational fluid dynamics (Succi 2001), life history processes and concepts and patterns from biogeography (Hubbell 2001, Bell 2001), evolution and aspects of selection (Hartl and Clark 1997), and integrates nutrient-limited growth and physiology (Pirt 1965, Droop 1983) among dimension of ecology and evolutionary science. 
I constructed simplex with the aim of simulating ecologically complex scenarios, from which the results could be used to test (*i*) predictions of ecological theory and (*ii*) the general influence of constraints and processes. 
Below, I provide detailed explanation of how hydrobide works, the data it quantifies and tracks, the theories and principles hydrobide integrates, and the analyses that can be conducted using the code we provide.

@@

**Source code**--To save space, I also refer the reader to the README.md file on the public simplex GitHub.com repository (https://github.com/LennonLab/simplex/blob/master/README.md) for descriptions of source code files and directories.

## Model description following the ODD Protocol
The ODD protocol is standard for describing individual-based models (Grimm et al. 2006). 
ODD stands for Overview, Design concepts, and Details. Here, I descibe simplex *largely* according to the ODD protocol.
The ODD protocol for simplex can also be found on the public GitHub repository at https://github.com/LennonLab/simplex

@@

I ran simplex on a Mid 2010 MacBook Pro (OS X 10.9.5) with a 2.4 GHz Intel Core 2 Duo processor and 4GB of Memory. This system probably represents a below average capacity for modern personal computers, which for this study, was desirable as simplex should be able to be ran on both personal computers and high capacity remote servers. I present results for time to completion and required memory in the Results.

@@

I thank Jay T. Lennon, Mario Muscarella, Xiao Xiao,

>>>>

---
title: "simplex: An individual-based modeling platform"
author: "TBD,
Dept. of Biology, University of Indiana, Bloomington"
geometry: margin=2.54cm
output: pdf_document
header-includes:
    - \usepackage{setspace}
    - \doublespacing
---

@@

Here, we present source code and a detailed description for an ecological IBM platform (called simplex) that simulates a broad range of ecological conditions, records information from individuals to the ecosystem, and provides computing code for analyzing output. This platform incorporates computational fluid dynamics (Succi 2001), life history processes and concepts and patterns from biogeography (Hubbell 2001, Bell 2001), evolution and aspects of selection (Hartl and Clark 1997), and integrates nutrient-limited growth and physiology (Pirt 1965, Droop 1983) among dimension of ecology and evolutionary science. 
We constructed simplex with the aim of simulating ecologically complex scenarios, from which the results could be used to test (*i*) predictions of ecological theory and (*ii*) the general influence of constraints and processes. 
Below, we provide detailed explanation of how hydrobide works, the data it quantifies and tracks, the theories and principles hydrobide integrates, and the analyses that can be conducted using the code we provide.

@@

**Source code**--To save space, we also refer the reader to the README.md file on the public simplex GitHub.com repository (https://github.com/LennonLab/simplex/blob/master/README.md) for descriptions of source code files and directories.

## Model description following the ODD Protocol
The ODD protocol is standard for describing individual-based models (Grimm et al. 2006). 
ODD stands for Overview, Design concepts, and Details. Here, we descibe simplex *largely* according to the ODD protocol.
The ODD protocol for simplex can also be found on the public GitHub repository at https://github.com/LennonLab/simplex

@@

We ran simplex on a Mid 2010 MacBook Pro (OS X 10.9.5) with a 2.4 GHz Intel Core 2 Duo processor and 4GB of Memory. This system probably represents a below average capacity for modern personal computers, which for this study, was desirable as simplex should be able to be ran on both personal computers and high capacity remote servers. We present results for time to completion and required memory in the Results.

@@

We thank Mario Muscarella and Xiao Xiao for fruitful discussions. **Grant number?**
